---
title: "W1 W2 pubertal timing psychopathology SCA"
author: "Michelle Byrne"
date: "3/30/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Set Working Directory
```{r Set Directory, message=FALSE, warning=FALSE, include=FALSE}
getwd()
#You should set this to the TAG directory on the CAS file server 
workdir='Z:/dsnlab/TAG/' 
```

```{r Load Data}
require(dplyr)
require(zoo)
# Load Data (Wave 1 and 2) first - see Marjolein's code for how this all got put together
data <- read.csv(file.path(workdir,"projects/W1_W2_pubertal_timing/Timing_allways.csv", fsep=""))

#!! - ADD PSYCHOPATHOLOGY DATA HERE - DIAGNOSES AND SYMPTOMS

```

# Model decisions and setup:

# 2 timepoints x N pubertal timing variables x N internalising outcome variables x control variables Y/N (OR possible combinations of N control variables) x impute or not = N models
```{r setup}
require(specr)
require (tidyverse)

# Example from specr !! - UPDATE BELOW WITH OUR DATA:
# Split into two SCA's: one with continuous outcomes, one with binary outcomes, then combine rows before plotting

setup_specs(y = c("y1"),               # We choose only one dependent variable
            x = c("x1", "x2"),         # We are not sure which independent variable is better
            model = c("lm"),           # We only estimate one type of model (linear model)
            controls = c("c1", "c2"))  # We include two control variable 

```


# The main function is run_specs() in which analytical choices are specified as arguments. The function plot_specs() can then be used to visualize the results.

# The function runs traditional linear regression models by default (i.e. when model = "lm" is provided as argument). However, customized model functions can be passed to the function, too.
```{r run_sca}
# !! - UPDATE BELOW WITH OUR DATA
# Split into two SCA's: one with continuous outcomes, one with binary outcomes, then combine rows before plotting

 logistic <- function(formula, data) {
  glm(formula = formula, 
      data = data, 
      family = binomial,
      control = glmerControl(optimizer = "bobyqa"))
}
                 
results <- run_specs(df = example_data, 
                     y = c("y1", "y2"), 
                     x = c("x1", "x2"), 
                     model = c("lm"), 
                     controls = c("c1", "c2"), 
                     subsets = list(group1 = unique(example_data$group1),
                                    group2 = unique(example_data$group2)))


```

```{r visualise}
# We can now plot a simple decision tree to understand how our analytical choices lead to a large number of specifications:

plot_decisiontree(results, 
                  legend = TRUE)

# basic summary of the entire specification curve:
summarise_specs(results)

# summary by specific groups and  statistics:
summarise_specs(results,                         # result data frame
                x, y,                            # grouping variables
                stats = lst(median, min, max))   # specific functions

# Plot specification curve analysis:
plot_specs(results, choices = c("x", "y", "controls", "subsets"))

#to produce respective boxplots:
plot_summary(results)
```

# Decompose the variance in the specification curve

#Finally, we can estimate how much variance in the specification curve is related to which analytical decisions. Therefore, we have to estimate a basic multilevel model without predictors and the analytical decisions as random effects (interactions could be included too). We then use the function icc_specs() to calculate a respective table or plot_variance() to visualize the distribution.
```{r}
# Estimate multilevel model 
library(lme4)
model <- lmer(estimate ~ 1 + (1|x)  + (1|y) + (1|controls) + (1|subsets), data = results)

# Get intra-class correlation
icc_specs(model) %>%
  mutate_if(is.numeric, round, 2)
#>        grp  vcov  icc percent
#> 1  subsets  0.79 0.04    3.62
#> 2 controls  0.05 0.00    0.23
#> 3        y 19.74 0.90   89.83
#> 4        x  0.43 0.02    1.95
#> 5 Residual  0.96 0.04    4.38

# Plot decomposition
plot_variance(model)

# Customize plots instructions:
# https://masurp.github.io/specr/articles/custom-plot.html
```

